Verifying Demonstrations

### 2018-02-06 paper/intro.tex

Alice is an activist who organizes a protest for some cause.
Eve is an autocrat who opposes Alice's cause.
Bob, Carol and many others participate in the protest against Eve.
One problem that has not yet been entirely solved is the crowd-counting 
problem, i.e.\ to verify how many participated in Alice's protest.
Our main goal is to provide a tool which prevents both Alice and Eve from 
cheating.

@@

After many demonstrations the count by police and that by the organizers 
differ\footnote{%
  This is actually quite natural, they have different goals.
  The organizers want to count everyone who ever participated.
  Police want to estimate the count at the peak of participation, due to crowd 
  control~\cite{2016DemonstrationsInSeoul}.
}, in some instances the difference can be hundreds of thousands.
There are numerous examples, e.g.\ the demonstrations in South 
Korea~\cite{2016DemonstrationsInSeoul}, Trump's 
inauguration~\cite{HowWillWeKnowTrumpInauguralCrowdSize} or the Women's Marches 
in the US~\cite{2017WomensMarchesInUS}, where there is difficulty in 
establishing the actual number of participants.
The methods for counting the crowds vary.
Most of the available methods lack precision, i.e.\ they have large error 
margins.
They can only give an estimate for a particular snapshot in time, e.g.\ at the 
peak of the event, not the cumulative participation count --- at least not 
without counting some people multiple times, which in turn increases the error 
of the estimation.
Finally, they also lack verifiability, i.e.\ everyone must trust the entity who
does the counting.
(We will discuss them in more detail in \cref{RelatedWork}.)

@@

We can make one important observation about this problem that has seemingly 
been ignored in the past: it is an adversarial setting.
Alice the activist has an incentive to increase the tallied number of 
participants, whereas Eve (and possibly other interests) have an incentive to 
decrease the tallied number of participants.
In this case we have two options:
either we trust Alice or Eve, or we must verify their claims.
We aim for verifiable claims.
To solve this problem, we need a verifiable participation count which is 
protected from Sybil attacks.

@@

In general, protesting is very similar to voting: both are many individuals 
expressing their opinion.
These opinions can be sensitive, hence we desire to have similar properties of 
verification and privacy for participation in a protest as there is for voting.

Voting has three requirements for 
verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{frame}
\begin{description}
  \item[Eligibility] anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability] anyone can verify that the result is according 
    to the cast votes.
  \item[Individual verifiability] every voter can verify that their vote is 
    included in the result.
\end{description}
\end{frame}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the 
participation count by counting the proofs.
The eligibility requirement is slightly different:
for protests the eligibility requirement must include temporal and spatial 
eligibility, i.e.\ that each proof of participation satisfies some temporal and 
spatial relation to the protest.
In essence, the proof must bind the person to the time and location of the 
protest.
We will define these more formally in \cref{Verifiability}.

@@

There are also three levels of 
privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{itemize}
  \item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
    individual vote.
  \item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
    provide any data that can be used as a proof of how the voter voted.
  \item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
    with a coercer to prove the vote was cast in any particular way.
\end{itemize}
We note that we cannot improve the privacy of participating protesters, if they 
are caught during a protest there is nothing we can do.
But if they are not caught in the act, then using our proposed tool should not 
incur any additional risk.
Thus we will adapt the idea of receipt freeness (see \cref{Privacy} for a 
detailed definition) to the protest context.
In essence, upon completing the protocol, Eve cannot link Alice to Alice's 
participation proof --- even with Alice's cooperation.

@@

>>>>

Alice is an activist who organizes a protest for some cause.
Eve is an autocrat who opposes Alice's cause.
Bob, Carol and many others participate in the protest against Eve.
One problem that has not yet been entirely solved is the crowd-counting 
problem, i.e.\ to verify how many participated in Alice's protest.

@@

After many demonstrations the count by police and that by the organizers 
differ\footnote{%
  This is actually quite natural, they have different goals.
  The organizers want to count everyone who ever participated.
  Police want to estimate the count at the peak of participation, due to crowd 
  control~\cite{2016DemonstrationsInSeoul}.
}, in some instances the difference can be hundreds of thousands.
There are numerous examples where there is difficulty in establishing the actual 
number of participants, e.g.:\@ the demonstrations against the president in 
South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration 
attendance~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March 
in the US~\cite{2017WomensMarchesInUS}, the demonstrations against changing the 
constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the 
independence of Catalonia~\cite{CataloniaDemonstrations}.
The methods for counting the crowds vary.
Most of the available methods lack precision, i.e.\ they have large error 
margins.
They can only give an estimate for a particular snapshot in time, e.g.\ at the 
peak of the event, not the cumulative participation count --- at least not 
without counting some people multiple times, which in turn increases the error 
of the estimation.
Finally, they also lack verifiability, i.e.\ everyone must trust the entity who
does the counting.
(We will discuss them in more detail in \cref{RelatedWork}.)

@@

We can make one important observation about this problem that has seemingly 
been ignored in the past: it is an adversarial setting.
Alice the activist has an incentive to increase the tallied number of 
participants, whereas Eve (and possibly other interests) have an incentive to 
decrease the tallied number of participants.
In this case we have two options:
either we trust Alice or Eve, or we must verify their claims.
Our main goal is to provide a scheme which prevents both Alice and Eve from 
cheating, i.e.\ we aim for verifiable claims.
To solve this problem, we need a verifiable participation count which is 
protected from Sybil attacks.

@@

In general, protesting is very similar to petitions, which in turn are similar 
to voting: all three are many individuals expressing their opinion.
These opinions can be sensitive, e.g.\ cause for discrimination or persecution, 
hence we desire to have similar properties of verification and privacy for 
verifying a protest as there is for voting.

Voting has (generally) three desirable requirements for 
verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{frame}
\begin{description}
  \item[Eligibility] anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability] anyone can verify that the result is according 
    to the cast votes.
  \item[Individual verifiability] every voter can verify that their vote is 
    included in the result.
\end{description}
\end{frame}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the 
participation count by counting the proofs.
The eligibility requirement is slightly different:
for protests the eligibility requirement must include temporal and spatial 
eligibility, i.e.\ that each proof of participation satisfies some temporal and 
spatial relation to the protest.
In essence, the proof must bind the person to the time and location of the 
protest.
We will define these more formally in \cref{Verifiability}.

@@

There are also three levels of 
privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{itemize}
  \item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
    individual vote.
  \item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
    provide any data that can be used as a proof of how the voter voted.
  \item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
    with a coercer to prove the vote was cast in any particular way.
\end{itemize}
We note that we cannot improve the privacy of participating protesters during 
the protest: if Alice is caught during a protest there is nothing we can do.
Actually, if there are several protests in the \emph{same location at the same 
  time}, Alice could blend into another crowd and argue that she participated in 
a different protest than she actually did --- and the counts would still be 
correct afterwards.
However, even if there is only one protest and she is not caught in the act, 
then using our proposed tool should not incur any additional risk.
Thus we need at least participation-proof privacy but receipt freeness (see 
\cref{Privacy} for a detailed definition) is desired.
In essence, upon completing the protocol, Eve cannot link Alice to Alice's 
participation proof --- even if she would compromise Alice's devices.

@@

We can achieve privacy, but not receipt freeness.
This means that there is a way for Eve to efficiently verify that Alice has 
participated.
However, this requires that Eve gets a copy of Alice's secret key so that she 
can simply re-do the (deterministic) computations on the same inputs --- the 
probability of collisions is negligible.

### 2018-02-06 paper/properties.tex

\begin{requirements}[V]
  \item\label{EligibilityVerif} Eligibility: anyone can verify that each 
    participation proof provides temporal and spatial eligibility and that it 
    has not been counted before.
    \begin{requirements}[]
    \item Temporal egligibility:%
      \label{CreatedAfterStart} prove that the data was created after the start of 
      the event;%
      \label{CreatedBeforeEnd} prove that the data was created before the end of 
      the event.
    \item Spatial eligibility:%
      \label{SpatiallyRelated} prove that the data is spatially related to the 
      physical location of the event.
    \item One-proof-per-person:%
      \label{CountOnce} prove that no individual can be counted more than once.
    \item Designated event:%
      \label{DesignatedEvent} prove that the data is designated for the event.
    \end{requirements}

@@

>>>>

\begin{requirements}[V]
  \item\label{EligibilityVerif} Eligibility: anyone can verify that each 
    participation proof provides temporal and spatial eligibility and that it 
    has not been counted before.
    \begin{requirements}
    \item Temporal egligibility:%
      \label{CreatedAfterStart} prove that the data was created after the start of 
      the event;%
      \label{CreatedBeforeEnd} prove that the data was created before the end of 
      the event.
    \item Spatial eligibility:%
      \label{SpatiallyRelated} prove that the data is spatially related to the 
      physical location of the event.
    \item One-proof-per-person:%
      \label{CountOnce} prove that no individual can be counted more than once.
    \item Designated event:%
      \label{DesignatedEvent} prove that the data is designated for the event.
    \end{requirements}

@@

There are two aspects of temporal eligibility.
The adversary can try to forge a witness for a future protest and the adversary 
can try to forge a witness for a past protest.

The first thing we want to do is to prevent Alice from collecting witnesses for 
a future protest.
For this, we introduce something we call a \emph{time-authenticator tag}.
This is an unpredictable value \(\tau_t\) which is published at time \(t\).
The idea is that it is difficult to guess \(\tau_t\) for a given \(t\) in 
advance, i.e.\ any use of \(\tau_t\) must have happened after time \(t\) with 
high probability.

\begin{definition}[Predicting the future]
  Let \(T_t = (\tau_i)_{i=0}^{t}\) be the sequence of time-authenticator tags up 
  until time \(t\), where \(\tau_i\in \Z_{2^\lambda}\) for all \(i\).
  (\(\lambda\) is the security parameter.)
  Let \A be \iac{PPT} adversary.
  The challenger gives \(T_{t-1}\) to \A.
  \A is allowed to query an oracle \(O\) which returns whether a guess is 
  correct or not.
  If \(\A^O(T_{t-1},1^\lambda)\) outputs \(\tau\) such that \(\tau = \tau_t\) 
  the adversary wins.
\end{definition}

We can see that if \(\tau_t\) is chosen uniformly randomly then the adversary's 
chance of winning will be
\begin{equation}
  \label{SuccessOfPrediction}
  \Prob{%
    \A^O(T_{t-1}, \lambda) = \tau_t
  } = \frac{p(\lambda)}{2^\lambda}
\end{equation}
for some polynomial \(p(\cdot)\).
This will be negligible for sufficiently a large \(\lambda\).

\begin{definition}[Collision]
  Given tag \(\tau\), probability of collision?
\end{definition}

\begin{definition}[Changing the past]
  Given a witness for time \(t\), change it to time \(t'\).
  \dots
\end{definition}

\begin{definition}[Forging past witnesses]
  \dots
\end{definition}
